Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-12-28 hscc2017/paper.tex
implement comment related to "Fig 3: clarifications #47"

Given a model for a plant in ANSI-C syntax as input (Steps 1--3), \tool
constructs a non-deterministic model to represent the plant family (Step~A),
and formulates a function (Step~B) using implementation details provided in
Steps~$2$ and $3$ to calculate the parameters of the controller to be
synthesized (Step~C).  Finally, \tool builds an intermediate ANSI-C code for
the digital system implementation, which is used as input for the CEGIS
engine (Step~D).

>>>>

Given a model for a plant in ANSI-C syntax as input (Steps 1--3), \tool
constructs a non-deterministic model to represent the plant family,
i.e., it addresses plant variations as interval sets (Step~A),
and formulates a function (Step~B) using implementation details provided in
Steps~$2$ and $3$ to calculate the parameters of the controller to be
synthesized (Step~C).  Note that \tool synthesizes the controller 
coefficients for the given implementation aspects, i.e., numerical
representation and realization form.  Finally, \tool builds an intermediate 
ANSI-C code for the digital system implementation, which is used as input 
for the CEGIS engine (Step~D).
